\documentclass[10pt]{article}
\usepackage[T1]{fontenc}
\usepackage{calc}
\usepackage{setspace}
\usepackage{multicol}

\usepackage{graphicx}
\usepackage{color}
\usepackage{rotating}
\usepackage{verbatim}
\usepackage{natbib}

\setlength{\voffset}{0in}
\setlength{\topmargin}{0pt}
\setlength{\hoffset}{0pt}
\setlength{\oddsidemargin}{0pt}
\setlength{\headheight}{0pt}
\setlength{\headsep}{.4in}
\setlength{\marginparsep}{0pt}
\setlength{\marginparwidth}{0pt}
\setlength{\marginparpush}{0pt}
\setlength{\footskip}{.1in}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}
\setlength{\parskip}{0pc}

\renewcommand{\baselinestretch}{1}

\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}
\newcommand{\prbf}[1]{\textbf{#1}}
\newcommand{\prit}[1]{\textit{#1}}
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqa}{\begin{eqnarray}}
\newcommand{\eeqa}{\end{eqnarray}}
\newcommand{\bdm}{\begin{displaymath}}
\newcommand{\edm}{\end{displaymath}}
\newcommand{\script}[1]{\begin{cal}#1\end{cal}}
%\newcommand{\citee}[1]{\citename{#1} (\citeyear{#1})}
\newcommand{\citee}[1]{\citet{#1}}
\newcommand{\h}[1]{\hat{#1}}
\newcommand{\ds}{\displaystyle}

\newcommand{\app}
{
\appendix
}

\newcommand{\appsection}[1]
{
\let\oldthesection\thesection
\renewcommand{\thesection}{Appendix \oldthesection}
\section{#1}\let\thesection\oldthesection
\renewcommand{\theequation}{\thesection\arabic{equation}}
\setcounter{equation}{0}
}

\pagestyle{plain}


\begin{document}

\begin{titlepage}
\begin{singlespace}
\title{Learning and Judgment Shocks in U.S. Business Cycles\footnote{I am thankful to Michael Plante and the participants of the Midwest Economics Association 2011 Annual meeting for valuable comments.  All errors are my own.}}
\date{\today}
\author{James Murray\footnote{\textit{Mailing address}: 1725 State St., La Crosse, WI  54601.  \textit{Phone number}: (608)406-4068.}\\
Department of Economics\\
University of Wisconsin - La Crosse\\
\textit{E-mail address}: jmurray@uwlax.edu}

\maketitle

\thispagestyle{empty}

\abstract{This paper examines the role of judgment shocks in combination with other structural shocks in explaining post-war economic volatility within the context of a New Keynesian model.  Agents form expectations using constant gain learning then augment these forecasts with judgment.  These judgments may be interpreted as a reaction to current news stories or policy announcements that would influence people's expectations.  I allow for the possibility that these judgments be informatively based on information about structural shocks, but judgment itself may also be subject to its own stochastic shocks.  I estimate a standard New Keynesian model that includes these shocks using Bayesian simulation methods.  To aid in identifying expectational shocks from other structural shocks I include data on professional forecasts along with data on output gap, inflation, and interest rates.}\newline  

\noindent \textit{Keywords}: Learning, judgment, add-factors, New Keynesian model, Metropolis-Hastings. \\
\noindent \textit{JEL classification}: C13, E31, E50.
\end{singlespace}
\end{titlepage}

\end{document}
